### 2023-03-13 main/chapter_2ljets.tex
begin table copy

@@

\subsubsection{Alternative \texorpdfstring{$\zjets$}{Z+jets}}
\label{sec:2ljets_zjets_alt}
As seen in Section~\ref{sec:2ljets_low}, the $\zjets$ sample comparison is
important to our results in SR-Low.
Its central yields are displayed in Figure~\ref{fig:2ljets_low_sr_or_cr_region}
in the union of \crz\ and SR-Low, which form a continuous region in $\mjj$.
Our central $\zjets$ samples use \sherpa~2.2.1~\cite{
Bothmann:2019yzt,
Gleisberg:2008ta,
ATL-PHYS-PUB-2016-003
}
at next-to-leading order for up to $4$ partonic jets, and leading order for
$5$ partonic jets.
In Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt} we compare this to our
alternative sample that simulates its hard scatter
with \madgraph\ (\amcatnlo~2.2.3~\cite{Alwall:2014hca}) at leading order with
up to four partonic jets, plugged into \pythia~8~\cite{Sjostrand:2014zea} for
showering and hadronization.
This \madgraph\ alternative sample simulates only $\mll > 40\,\eV[G]$, so in
regions allowing $\mll$ outside this we evaluate relative variations and
scale them up to the central yield.
The plots in Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt} show statistical
error bars only; the alternative sample has larger statistical errors since
it contains around one sixth as many simulated events as the central sample,
and that difference is not countered by their different weight distributions
in this region.

@@

\subsubsection{Alternative \diboson}
\label{sec:2ljets_diboson_alt}
When executing this analysis project, no complete alternative \diboson\ samples
were available in the specific post-processed format required for our analysis'
software framework.
Our central \diboson\ samples are simulated with \sherpa~2.2.2 at NLO with up
to six electroweak vertices, and although \diboson\ sample comparisons are
conditionally recommended by internal
documentation~\cite{atlas_twiki_susytheoretical}, we failed to acquire
alternative samples for this comparison.
This limitation is in part a result of how \atlas\ and our local SUSY group has
decided to allocate its limited resources, and quite reasonably so, since
full simulation and data derivation is expensive in computation and data
storage regards, and \diboson\ processes are relatively rare.
Instead, we followed advice to use the cheaper alternative set of small,
truth-level samples, that were simulated with the same \sherpa\ setup but with
varied parameters to assess uncertainties in the modelling of parton showers.

>>>>

\begin{sidewaystable}[tp]
\begin{center}
\scriptsize
\begin{tabular}{llllll}
Physical process &  Generator  & Parton & Cross-section & Tune & PDF set\\
                &             & shower & order in pQCD &      &
\\[0.2em]
\hline
\\[0.2em]
$\ttbar$~\cite{ATL-PHYS-PUB-2016-004}         & \powhegbox\,v2~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd}    & \pythia\,8.230~\cite{Sjostrand:2014zea} & NNLO+NNLL~\cite{ttbarxsec1,ttbarxsec2,ttbarxsec3,ttbarxsec4,ttbarxsec5}                   & A14~\cite{ATL-PHYS-PUB-2014-021}   & \textsc{NNPDF2.3lo}~\cite{Ball:2012cx}\\
$Wt$~\cite{ATL-PHYS-PUB-2016-004}  & \powhegbox\,v2    & \pythia\,8.230 & NNLO+NNLL~\cite{Kidonakis:2010b,Kidonakis:2010tc,Kidonakis:2011wy,Frederix:2012dh}        &A14    & \textsc{NNPDF3.0nlo}~\cite{Ball:2014uwa}\\
$VV$~\cite{ATL-PHYS-PUB-2016-002} & \sherpa\,2.2.2~\cite{Bothmann:2019yzt} & \sherpa\,2.2.2 & NLO~\cite{diboson1,diboson2} & \textsc{Sherpa}\ default & \textsc{NNPDF3.0nnlo} \\
$Z/\gamma^{*}(\rightarrow \ell \ell)$\,+\,jets~\cite{ATL-PHYS-PUB-2016-003}& \sherpa\,2.2.1           & \sherpa\,2.2.1  &NNLO~\cite{DYNNLO1,DYcrosssection}       & \textsc{Sherpa}\ default     &\textsc{NNPDF3.0nnlo}\\
Higgs ($\ttbar h$) & \powhegbox\,v2    & \pythia\,8.230 & NLO~\cite{deFlorian:2016spz} & A14    & \textsc{NPDF2.3lo}\\
Higgs (VBF, $Vh$) & \powhegbox\,v2     & \pythia\,8.212 & NNLO~\cite{deFlorian:2016spz} & AZNLO~\cite{STDM-2012-23} &  \textsc{CTEQ6L1}~\cite{Pumplin:2002vw} \\
Higgs (ggF) & \powhegbox\,v2     & \pythia\,8.212 & NNNLO~\cite{deFlorian:2016spz} & AZNLO & \textsc{CTEQ6L1} \\
$ttt$, $tttt$, $\ttbar$\,+\,$WW$ & \amcatnlo~\cite{Alwall:2014hca} & \pythia\,8.186~\cite{Skands:2014pea} & NLO~\cite{Frederix:2017wme,Alwall:2014hca} & A14 & \textsc{NNPDF2.3lo}\\
$\ttbar$\,+\,$V$~\cite{ATL-PHYS-PUB-2016-005,Garzelli:2012bn}& \amcatnlo        & \pythia\,8.210 & NLO~\cite{Campbell:2012,Lazopoulos:2008,Alwall:2014hca} & \textsc{A14} & \textsc{NNPDF2.3lo}\\
$VVV$~\cite{ATL-PHYS-PUB-2016-002} & \sherpa\,2.2.2 & \sherpa\,2.2.2 &  NLO~\cite{Bothmann:2019yzt} & \textsc{Sherpa}\ default     & \textsc{NNPDF3.0nnlo}\\
\end{tabular}
\caption{%
Caption TODO
% TODO define VBF
% TODO rewrite
% Simulated background event samples used in this analysis with the corresponding matrix element and parton shower generators,
% cross-section order in perturbative QCD used to normalize the event yield, underlying-event tune and PDF set.
% $V$ represents either a $W$ or $Z$ boson.%
}
\label{tab:2ljets_paper_mc}
\end{center}
\end{sidewaystable}

@@

\subsubsection{Alternative \texorpdfstring{$\zjets$}{Z+jets}}
\label{sec:2ljets_zjets_alt}
As seen in Section~\ref{sec:2ljets_low}, the $\zjets$ sample comparison is
important to our results in SR-Low.
Its central yields are displayed in Figure~\ref{fig:2ljets_low_sr_or_cr_region}
in the union of \crz\ and SR-Low, which form a continuous region in $\mjj$.
Our central $\zjets$ samples use \sherpa\,2.2.1~\cite{
Bothmann:2019yzt,
Gleisberg:2008ta,
ATL-PHYS-PUB-2016-003
}
at next-to-leading order for up to $4$ partonic jets, and leading order for
$5$ partonic jets.
In Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt} we compare this to our
alternative sample that simulates its hard scatter
with \madgraph\ (\amcatnlo~2.2.3~\cite{Alwall:2014hca}) at leading order with
up to four partonic jets, plugged into \pythia~8~\cite{Sjostrand:2014zea} for
showering and hadronization.
This \madgraph\ alternative sample simulates only $\mll > 40\,\eV[G]$, so in
regions allowing $\mll$ outside this we evaluate relative variations and
scale them up to the central yield.
The plots in Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt} show statistical
error bars only; the alternative sample has larger statistical errors since
it contains around one sixth as many simulated events as the central sample,
and that difference is not countered by their different weight distributions
in this region.

@@

\subsubsection{Alternative \diboson}
\label{sec:2ljets_diboson_alt}
When executing this analysis project, no complete alternative \diboson\ samples
were available in the specific post-processed format required for our analysis'
software framework.
Our central \diboson\ samples are simulated with \sherpa\,2.2.2 at NLO with up
to six electroweak vertices, and although \diboson\ sample comparisons are
conditionally recommended by internal
documentation~\cite{atlas_twiki_susytheoretical}, we failed to acquire
alternative samples for this comparison.
This limitation is in part a result of how \atlas\ and our local SUSY group has
decided to allocate its limited resources, and quite reasonably so, since
full simulation and data derivation is expensive in computation and data
storage regards, and \diboson\ processes are relatively rare.
Instead, we followed advice to use the cheaper alternative set of small,
truth-level samples, that were simulated with the same \sherpa\ setup but with
varied parameters to assess uncertainties in the modelling of parton showers.
